Modal type theory based on the intuitionistic epistemic logic

### 2018-02-13 article.tex
modified comments in proofs

\begin{lemma} Properties of $\eta$:

@@

$\begin{array}{lll}
& \ast_{\hat{A},\hat{B}} \circ (\eta_{\hat{A}} \times \eta_{\hat{B}}) = & \\
& \text{By unfolding} & \\
& [q, {\bf let \: pure \:} x, y = \pi_1 q, \pi_2 q {\: \bf in \:} \langle x, y \rangle] \circ [p, \langle {\bf pure \:} (\pi_1 p), {\bf pure \:} (\pi_2 p) \rangle] = & \\
& \text{Composition}& \\
& [p, {\bf let \: pure \:} x, y = \pi_1 q, \pi_2 q {\: \bf in \:} \langle x, y \rangle [q := \langle {\bf pure \:} (\pi_1 p), {\bf pure \:} (\pi_2 p) \rangle]] = & \\
& \text{By substitution}& \\
& [p, {\bf let \: pure \:} x, y = \pi_1 (\langle {\bf pure \:} (\pi_1 p), {\bf pure \:} (\pi_2 p) \rangle), \pi_2 (\langle {\bf pure \:} (\pi_1 p), {\bf pure \:} (\pi_2 p) \rangle) {\: \bf in \:} \langle x, y \rangle] = & \\
& \text{Reduction rules}& \\
& [p, {\bf let \: pure \:} x, y = {\bf pure \:} (\pi_1 p), {\bf pure \:} (\pi_2 p) {\: \bf in \:} \langle x, y \rangle] = & \\
& \text{Reduction rule}& \\
& [p, {\bf pure \:} (\langle x,y \rangle [x := \pi_1 p, y := \pi_2 p])] = & \\
& \text{Substitution}& \\
& [p, {\bf pure \:} \langle \pi_1 p, \pi_2 p \rangle] = & \\
& \text{$\eta$-reduction}& \\
& [p, {\bf pure \:} p] =& \\
& \text{By definition}& \\
& \eta_{\hat{A} \times \hat{B}}&
\end{array}$

@@

$\begin{array}{lll}
&\text{fmap } \alpha_{\hat{A},\hat{B},\hat{C}} \circ \tau_{\hat{A} \times \hat{B}, \hat{C}} = & \\
&[q, {\bf let \: pure \:} r = q {\: \bf in \:}  \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle] \: \circ & \\
&\quad\quad\quad\quad \circ \: [p, {\bf \: let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle \langle x,y \rangle, z \rangle] = & \\
&[p, {\bf let \: pure \:} r = q {\: \bf in \:}  \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle & \\
&\quad\quad\quad\quad [q := {\bf \: let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle \langle x,y \rangle, z \rangle]] = & \\
&[p, {\bf let \: pure \:} r = ({\bf let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle \langle x,y \rangle, z \rangle) & \\
&\quad\quad\quad\quad {\: \bf in \:} \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle] = & \\
&[p, {\bf let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:}  \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle & \\
&\quad\quad\quad\quad [r := \langle \langle x,y \rangle, z \rangle]] = & \\
&[p, {\bf let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle x, \langle y, z \rangle \rangle]&
\end{array}$

@@

>>>>

\begin{lemma} Naturality and coherence for $\eta$:

@@

$\begin{array}{lll}
& \ast_{\hat{A},\hat{B}} \circ (\eta_{\hat{A}} \times \eta_{\hat{B}}) = & \\
& \quad\quad\quad\quad\quad\quad \text{By unfolding} & \\
& [q, {\bf let \: pure \:} x, y = \pi_1 q, \pi_2 q {\: \bf in \:} \langle x, y \rangle] \circ [p, \langle {\bf pure \:} (\pi_1 p), {\bf pure \:} (\pi_2 p) \rangle] = & \\
& \quad\quad\quad\quad\quad\quad \text{Composition}& \\
& [p, {\bf let \: pure \:} x, y = \pi_1 q, \pi_2 q {\: \bf in \:} \langle x, y \rangle [q := \langle {\bf pure \:} (\pi_1 p), {\bf pure \:} (\pi_2 p) \rangle]] = & \\
& \quad\quad\quad\quad\quad\quad \text{By substitution}& \\
& [p, {\bf let \: pure \:} x, y = \pi_1 (\langle {\bf pure \:} (\pi_1 p), {\bf pure \:} (\pi_2 p) \rangle), \pi_2 (\langle {\bf pure \:} (\pi_1 p), {\bf pure \:} (\pi_2 p) \rangle) {\: \bf in \:} \langle x, y \rangle] = & \\
& \quad\quad\quad\quad\quad\quad \text{Reduction rules}& \\
& [p, {\bf let \: pure \:} x, y = {\bf pure \:} (\pi_1 p), {\bf pure \:} (\pi_2 p) {\: \bf in \:} \langle x, y \rangle] = & \\
& \quad\quad\quad\quad\quad\quad \text{Reduction rule}& \\
& [p, {\bf pure \:} (\langle x,y \rangle [x := \pi_1 p, y := \pi_2 p])] = & \\
& \quad\quad\quad\quad\quad\quad \text{Substitution}& \\
& [p, {\bf pure \:} \langle \pi_1 p, \pi_2 p \rangle] = & \\
& \quad\quad\quad\quad\quad\quad \text{$\eta$-reduction}& \\
& [p, {\bf pure \:} p] =& \\
& \quad\quad\quad\quad\quad\quad \text{By definition}& \\
& \eta_{\hat{A} \times \hat{B}}&
\end{array}$

@@

$\begin{array}{lll}
&\text{fmap } \alpha_{\hat{A},\hat{B},\hat{C}} \circ \tau_{\hat{A} \times \hat{B}, \hat{C}} = & \\
&[q, {\bf let \: pure \:} r = q {\: \bf in \:}  \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle] \: \circ & \\
&\quad\quad\quad\quad \circ \: [p, {\bf \: let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle \langle x,y \rangle, z \rangle] = & \\
&\quad\quad\quad\quad\quad\quad \text{Composition}& \\
&[p, {\bf let \: pure \:} r = q {\: \bf in \:}  \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle & \\
&\quad\quad\quad\quad [q := {\bf \: let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle \langle x,y \rangle, z \rangle]] = & \\
&\quad\quad\quad\quad\quad\quad \text{Substitution and reduction}& \\
&[p, {\bf let \: pure \:} r = ({\bf let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle \langle x,y \rangle, z \rangle) & \\
&\quad\quad\quad\quad {\: \bf in \:} \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle] = & \\
&\quad\quad\quad\quad\quad\quad \text{$\beta$-reduction rule}& \\
&[p, {\bf let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:}  \langle \pi_1 (\pi_1 r), \langle \pi_2 (\pi_1 r), \pi_2 r \rangle \rangle & \\
&\quad\quad\quad\quad [r := \langle \langle x,y \rangle, z \rangle]] = & \\
&\quad\quad\quad\quad\quad\quad \text{$\beta$-reduction rule}& \\
&[p, {\bf let \: pure \:} x,y,z = {\bf pure\:} (\pi_1 (\pi_1 p)), {\bf pure \:} (\pi_2 (\pi_1 p)), \pi_2 p {\: \bf in \:} \langle x, \langle y, z \rangle \rangle]&
\end{array}$

@@

$\begin{array}{lll}
&[p, {\bf let \: pure \:} x, y, z = ({\bf pure \:} \pi_1 p, {\bf let \: pure \:} p^{'} = \pi_2 p {\: \bf in \:} \pi_1 p^{'}, {\bf let \: pure \:} p^{'} = \pi_2 p {\: \bf in \:} \pi_2 p^{'}) & \\
&\quad\quad\quad\quad {\: \bf in \:} \langle x, \langle y, z \rangle\rangle] = & \\
&\quad\quad\quad\quad\quad\quad \text{Substitution and reduction}& \\
&[p, {\bf let \: pure \:} x, p^{'}, z = ({\bf pure \:} \pi_1 p, \pi_2 p, {\bf let \: pure \:} p^{'} = \pi_2 p {\: \bf in \:} \pi_2 p^{'}) {\: \bf in \:} \langle x, \langle \pi_1 p^{'}, z \rangle\rangle] = & \\
&\quad\quad\quad\quad\quad\quad \text{Substitution and reduction}& \\
&[p, {\bf let \: pure \:} x, p^{'} = {\bf pure \:} \pi_1 p, \pi_2 p {\: \bf in \:} \langle x, \langle \pi_1 p^{'}, \pi_2 p^{'} \rangle\rangle]&
\end{array}$

$\begin{array}{lll}
&\tau_{\hat{A}, \hat{B} \times \hat{C}} \circ (id_{\hat{A}} \times \tau_{\hat{B}, \hat{C}}) \circ \alpha_{\hat{A}, \hat{B}, {\bf K}\hat{C}} = & \\
&\quad\quad\quad\quad\quad\quad \text{Unfolding}& \\
&\tau_{\hat{A}, \hat{B} \times \hat{C}} \circ [q, \langle \pi_1 q, {\bf let \: pure \:} y, z = {\bf pure \:} (\pi_1 (\pi_2 q)), \pi_2 (\pi_2 q) {\: \bf in \:} \langle y, z \rangle \rangle] \: \circ & \\
&\quad\quad\quad\quad \circ \: [p, \langle \pi_1 (\pi_1 p), \langle \pi_2 (\pi_1 p), \pi_2 p \rangle \rangle] = & \\
&\quad\quad\quad\quad\quad\quad \text{Composition}& \\
&\tau_{\hat{A}, \hat{B} \times \hat{C}} \circ [p, \langle \pi_1 q, {\bf let \: pure \:} y, z = {\bf pure \:} (\pi_1 (\pi_2 q)), \pi_2 (\pi_2 q) {\: \bf in \:} \langle y, z \rangle \rangle & \\
&\quad\quad\quad\quad [q := \langle \pi_1 (\pi_1 p), \langle \pi_2 (\pi_1 p), \pi_2 p \rangle \rangle]] = & \\
&\quad\quad\quad\quad\quad\quad \text{Substitution and reduction}& \\
&\tau_{\hat{A}, \hat{B} \times \hat{C}} \circ [p, \langle \pi_1 (\pi_1 p), {\bf let \: pure \:} y, z = {\bf pure \:} \pi_2 (\pi_1 p), \pi_2 p {\: \bf in \:} \langle y, z \rangle \rangle] = & \\
&\quad\quad\quad\quad\quad\quad \text{Composition}& \\
&[r, {\bf let \: pure \:} x, p^{'} = {\bf pure \:} \pi_1 r, \pi_2 r {\: \bf in \:} \langle x, \langle \pi_1 p^{'}, \pi_2 p^{'} \rangle\rangle] \: \circ & \\
&\quad\quad\quad\quad \circ \: [p, \langle \pi_1 (\pi_1 p), {\bf let \: pure \:} y, z = {\bf pure \:} \pi_2 (\pi_1 p), \pi_2 p {\: \bf in \:} \langle y, z \rangle \rangle] = & \\
&\quad\quad\quad\quad\quad\quad \text{Substitution and reduction}& \\
&[p, {\bf let \: pure \:} x, p^{'} = ({\bf pure \:} (\pi_1 (\pi_1 p)), {\bf let \: pure \:} y, z = ({\bf pure \:} \pi_2 (\pi_1 p), \pi_2 p {\: \bf in \:} \langle y, z \rangle \rangle) & \\
&\quad\quad\quad\quad {\: \bf in \:} \langle x, \langle \pi_1 p^{'}, \pi_2 p^{'} \rangle\rangle ] = & \\
&\quad\quad\quad\quad\quad\quad \text{Reduction}& \\
&[p, {\bf let \: pure \:} x,y,z = {\bf pure \:} (\pi_1 (\pi_1 p)), {\bf pure \:} \pi_2 (\pi_1 p), \pi_2 p {\: \bf in \:} \langle x, \langle \pi_1 p^{'}, \pi_2 p^{'} \rangle\rangle [p^{'} := \langle y, z \rangle]] = & \\
&\quad\quad\quad\quad\quad\quad \text{Substitution and reduction}& \\
&[p, {\bf let \: pure \:} x,y,z = {\bf pure \:} (\pi_1 (\pi_1 p)), {\bf pure \:} \pi_2 (\pi_1 p), \pi_2 p {\: \bf in \:} \langle x, \langle y, z \rangle\rangle]&
\end{array}$

2) Easy
